---
title: "workshop_7"
author: "Jacob Coggshall"
date: "2023-05-17"
output: html_document
---
put it in the global message when you make an R markdown for midterm
message = false, eval = false, echo = false, warning = false

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
# should haves
library(tidyverse)
library(here)
library(lterdatasampler)
# would be nice to have
library(performance)
library(broom)
library(flextable)
library(ggeffects)
library(car)
library(naniar)
```

#Linear models

how does stem length _predict_ stem dry mass?

```{r filtering_data}
maples_data <- hbr_maples|>
  filter(year == 2003 & watershed == "Reference")
```

#Visualizing missing data:

```{r missing_data_vis}
gg_miss_var(maples_data)
```

Create an exploratory data visualization 

```{r explore-data-vis}
ggplot(data = maples_data, aes(x = stem_length, y = stem_dry_mass)) + geom_point()
```

Lets try a model:

```{r linear-model-maples}
maples_model <- lm(stem_dry_mass ~ stem_length, maples_data)

maples_model
```
Check Assumptions:
1.linear relationship netween variables: yes! (used exploratory data visualiazation to check that)

2.independence of error: yes! (making assumption based on how data was collected)

3.homoskedasticity of errors: yes! (making that decisionfrom residuals vs fitted plot/scale-location plots)

4. normally distributed errors:yes! (looking at QQ plot of residuals)

```{r checking_assumptions}
par(mfrow = c(2, 2))
plot(maples_model)
```

turn of 2x2 grid:

```{r turning_off_the_grid}
dev.off()
```

#Putting things together to communicate

## model predictions

```{r pulling_out_predictions}
predictions <- ggpredict(maples_model, terms = "stem_length")


```

plot predictions:

```{r plot_predictions}
plot_predictions <- ggplot(data = maples_data, aes(x = stem_length, y = stem_dry_mass)) +
  #first plot underlying data
  geom_point() +
  #plotting model predictions from "predictions" object using ggeffects
  geom_line(data = predictions, aes(x = x, y = predicted), color = "blue", linewidth = 1) +
  #plot the confidence interval around model estimates
  geom_ribbon(data = predictions,aes(x = x, y = predicted, ymin = conf.low, ymax = conf.high), alpha = 0.2)

plot_predictions

```

## create tables

```{r model_summary_table}
model_summary <- summary(maples_model)

model_squares <- anova(maples_model)
```

making a table

```{r}
model_squares_table <- tidy(model_squares)|>
  mutate(p.value = case_when(
         p.value < 0.001 ~ "< 0.001"))|>
  flextable()|>
  set_header_labels(df = "Degrees of Freedom",
                    sumsq = "Sum of Squares")
model_squares_table
```

